%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {OAK Network} % Organization
    {Remote} % Location
    {May. 2022 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced annual infrastructure costs by over \$200,000 leveraging lower cost, bare metal servers where it made sense.}
        \item {Maintained blockchain servers using Terraform and Ansible.}
        \item {Unified the developer deployment experience using Github Actions to generate repeatable artifacts, reducing hands-on time during deployments.}
        \item {Developed blockchain code in Rust.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Lead Software Engineer} % Job title
    {benefitbay™} % Organization
    {Remote} % Location
    {Jul. 2021 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned, led, and assisted in development efforts bringing a legacy application running Ruby 2.3 and Rails 3.1 up to Ruby 2.7 and Rails 7.0.}
        \item {Maintained AWS infrastructure as code using Terraform to provide delivery of web application as a Docker container.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer, Senior Software Engineer} % Job title
    {BOLD PENGUIN} % Organization
    {Remote} % Location
    {Jul. 2019 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and developed new features for multiple large applications written in Ruby on Rails with AngularJS front-ends.}
        \item {Coordinated cross-team features to support enterprise customers.}
        \item {Facilitated developer experience by working on an extra-curricular team providing a Golang CLI tool to assist in day-to-day operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Information Technologist III, II, I} % Job title
    {Michigan State University} % Organization
    {East Lansing, Michigan} % Location
    {May. 2012 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored cross team developers in better software development practices including version control, automated testing, and CI/CD usage.}
        \item {Deployed Ruby and Javascript APIs to AWS using Cloudformation, Terraform, and custom tooling.}
        \item {Developed and maintained multiple greenfield Ruby on Rails API applications with RESTful and GraphQL interfaces.}
        \item {Maintained code written in C, Bash, Javascript, Perl, PHP, Python and other languages.}
        \item {Administered Linux and Unix servers hosting services including LPRNG, MySQL, Kerberos, Shibboleth, and Apache.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Director, Software Engineer} % Job title
    {DriveOnGroup} % Organization
    {Lansing, Michigan} % Location
    {Jan. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated local and offshore development talent building native mobile web applications backed by APIs}
        \item {Isolated and corrected performance issues preventing API from delivering necessary information to mobile front-ends.}
        \item {Migrated API service from a single node with no redundancy to an auto-scaling AWS Elastic Beanstalk deployment.}
        \item {Developed Ruby on Rails API for scheduling and pairing drivers with riders.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Consultant} % Job title
    {p5dev, LLC} % Organization
    {Remote} % Location
    {Nov. 2006 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked directly with small business owners to explore custom software solutions that fit their needs.}
        \item {Built web applications using Perl, PHP, CSS, and Javascript.}
        \item {Maintained custom Linux and Windows servers used for hosting web applications.}
        \item {Administered Apache and MySQL applications to support custom written software.}
        \item {Integrated with modern and legacy software including LDAP, AS/400, and DB2}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
